\subsection{Logical Form and Equivalence}
\hrulefill
\subsubsection*{Arguments}

\paragraph*{Definition}
An arguement is a sequence of statements aimed at demonstrating the truth of an assertion.
\begin{itemize}
    \item The assertion at the end of the sequence is called the conclusion.
    \item The statements that support the conclusion are called premises.
    \item If the premises are true, the conclusion must also be true.
\end{itemize}

\paragraph*{Example}
\begin{itemize}
    \item If student A is a math major or student A is a computer science major,
    \item Then student A will take Discrete Math.
\end{itemize}

\subsubsection*{Logical Statements}
\paragraph*{Definition}
A logical statement is a declarative sentence that is either true or false, but not both.\\
\begin{itemize}
    \item Not $p$: \quad $\neg p$
    \item $p$ and/but $q$: \quad $p \land q$
    \item $p$ or $q$: \quad $p \lor q$
    \item Neither $p$ nor $q$: \quad $\neg p \land \neg q$
\end{itemize}

\paragraph*{Example}
h = healthy, w = wealthy, s = wise\\
\begin{itemize}
    \item John is healthy and wealthy but not wise. 
    \begin{itemize}
        \item $\quad (h \land w) \land \neg s$
    \end{itemize}
    \item John is neither wealthy nor wise, but he is healthy
    \begin{itemize}
        \item $\quad (\neg w \land \neg s) \land h$
    \end{itemize} 
\end{itemize}

\subsubsection*{Equivalent Statements}
\paragraph*{Definition}
Two logical statements are equivalent if they have the same truth tables, denoted:
\begin{equation*}
    p \equiv q
\end{equation*}

\paragraph*{De Morgan's Laws}
The negation ($\neg$) of an and statement is logically equivalent to the or statement of the negations. Similarly,
the negation of an or statement is logically equivalent to the and statement of the negations. 
\begin{itemize}
    \item $\neg (p \land q) \equiv \neg p \lor \neg q$
    \item $\neg (p \lor q) \equiv \neg p \land \neg q$
\end{itemize}

\paragraph*{Tautological and Condtradictory Statements}
\begin{itemize}
    \item A tautological statement is a statement that is always true.
    \item A contradictory statement is a statement that is always false.
\end{itemize}

